\thetitle

### 2008-06-26 paper.tex
Removing done TODOs, work on results.

% TODO: update roadmap paragraph.

@@

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the composite behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\nicefrac{1}{2}$.

@@

% TODO: remove mixed conditional from plots.
\input{figures/box_plots}

@@

Finally, we turn to the conditional models. These demonstrate neither exceptionally good nor exceptionally bad behavior. That the conditional models should be similar to the \model{full marginal} model but somewhat more realistic is entirely expected: conditioning is a restricted form of marginal modeling, where each group of flows has its own marginal distribution. In these cases, the flows are grouped by source or by destination.
Neither source nor destination conditioning appears to out-perform the other:
they perform identically in each case;
neither is perfect, but both are better in general than any marginal or uniform model.
The node-conditional models tend to err in the same direction as the \model{full marginal} model, but in a few cases where the aspects of marginality lead to errors in different directions, the outcome follows one of the aspects more than others.
In the case of received throughput, for example, the \model{packet marginal} tendency to overestimate error overshadows the tendency of the other marginal aspects to underestimate.

% TODO: rerun the mixed model simulations.

>>>>

@@

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish, for example, to make the behavior of each flow a weighted average of the composite behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\nicefrac{1}{2}$.

@@

\input{figures/box_plots}

@@

Finally, we turn to the conditional models. These demonstrate neither exceptionally good nor exceptionally bad behavior. That the conditional models should be similar to the \model{full marginal} model but somewhat more realistic is entirely expected: conditioning is a restricted form of marginal modeling, where each group of flows has its own marginal distribution. In these cases, the flows are grouped by source or by destination.
Neither source nor destination conditioning appears to out-perform the other:
they perform identically in each case;
neither is perfect, but both are better in general than any marginal or uniform model.
The \model{source/dest. conditional} models tend to err in the same direction as the \model{full marginal} model, but in a few cases where the aspects of marginality lead to errors in different directions, the outcome follows one of the aspects more than others.
In the case of received throughput, for example, the \model{packet marginal} tendency to overestimate error overshadows the tendency of the other marginal aspects to underestimate.
Overall, we see that the conditional models are more realistic than other models, but this is effect occurs only as the number of nodes---\latin{i.e.} the number of conditioning classes---approaches the full rank of the original traffic matrix.
In our discussion, we present and demonstrate a far more compelling method of reducing and simplifying the representation of the behavior of large collections of flows.
